NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-01-25 Manuscript/manuscriptPS.tex
Update density profiles

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for the computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{Check and report all the counterions. There may be some simulation data 
    sets with both Na+ and K+ ions?} \\
  \todo{CHARMM36-UA point for alpha in wrong place?} \\
  \todo{MacRog POPS data missing. The equilibration yet to be checked, thought.} \\
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with  
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?} \\
  \todo{Lipid17 results should be added.} \\
  \todo{We should also add CHARMM36 POPS ran with K counterions: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1\#issuecomment-308570874}
\end{figure}

@@

>>>>

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers without additional ions}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for the computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{Check and report all the counterions. There may be some simulation data 
    sets with both Na+ and K+ ions?} \\
  \todo{CHARMM36-UA point for alpha in wrong place?} \\
  \todo{MacRog POPS data missing. The equilibration yet to be checked, thought.} \\
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with  
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?} \\
  \todo{Lipid17 results should be added.} \\
  \todo{We should also add CHARMM36 POPS ran with K counterions: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1\#issuecomment-308570874}
\end{figure}

@@

In contrast to PC lipids discussed previously \cite{botan15,catte16},
systems with negatively charged lipids always contains counterions.
Since the ion binding changes the headgroup order parameters \cite{seelig87,catte16},
the counterion distribution have to be taken into account also
when additional ions are not present.
The Na+ density profiles from different simulation are shown in Fig. \ref{NAdensPOPS}.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/NAdensPOPS.eps}
  \caption{\label{NAdensPOPS}
    Sodium density of POPS lipid bilayer along the membrane normal from
    simulations with different force fields.
  }
\end{figure}
